---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bis620.2022

<!-- badges: start -->
[![R-CMD-check](https://github.com/sidc2115/bis620.2022/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/sidc2115/bis620.2022/actions/workflows/R-CMD-check.yaml)
[![lint](https://github.com/sidc2115/bis620.2022/actions/workflows/lint.yaml/badge.svg)](https://github.com/sidc2115/bis620.2022/actions/workflows/lint.yaml)
[![test-coverage](https://github.com/sidc2115/bis620.2022/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/sidc2115/bis620.2022/actions/workflows/test-coverage.yaml)
[![codecov](https://codecov.io/gh/sidc2115/bis620.2022/branch/main/graph/badge.svg?token=E3EZ0R3IMQ)](https://codecov.io/gh/sidc2115/bis620.2022)
<!-- badges: end -->

The goal of bis620.2022 is to analyse the accelerometry data. The analysis 
is by way of making time-series plots from the data. The plots are in three
dimensions. The package can also be used to create spectral signatures using
the modulus of the Fourier coefficients in the different dimensions.

[Coverage Page](https://codecov.io/gh/sidc2115/bis620.2022)

[Lint Results](https://github.com/sidc2115/bis620.2022/actions/workflows/lint.yaml)

## Installation

You can install the development version of bis620.2022 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sidc2115/bis620.2022")
```

## Example

Here is a simple use of the package in plotting the spectral signatures:

```{r example1}
library(bis620.2022)

data(ukb_accel)
ukb_accel[1:500, ]|>
  spectral_signature(take_log = TRUE)|>
  accel_plot()
```

Here we use the package to plot time-series data:
```{r example2}
accel_plot(ukb_accel[1:500, ])
```

